---
title: "CARNIVAL Analysis Report"
output: html_document
params:
  analysis_expl: ""
  doro_custom: "**NOT** run."
  organism: ""
  minsize: ""
  confidence_level: ""
  method: ""
  pro_custom: "**NOT** included in the analysis."
  top: ""
  perm: ""
  omni: "**NOT** loaded."
  targets: "**NOT** selected."
  solver: "**NOT** selected"
  pea_custom: "the enrichment part has **NOT** been run."
  pea_explanation: ""
  pea_expl_barplot: ""
  pea_expl_volcano: ""
  carnival_network: NA
  barplot: NA
  volcano: NA
  active_pea: "FALSE"
---
    
[CARNIVAL](https://saezlab.github.io/CARNIVAL/) (CAusal Reasoning for Network identification using Integer VALue programming) reconstructs signalling networks from downstream TF activities by finding the upstream regulators ( [Liu et al., 2019](https://www.nature.com/articles/s41540-019-0118-z) ). Given a directed prior-knowledge network (PKN) of protein-protein interactions, which can also be signed, CARNIVAL identifies a subnetwork that explains the activities of transcription factors through potential perturbed intermediate genes.

### The analysis

`r params$analysis_expl`

**DoRotEA** (_measObj_) was `r params$doro_custom`

`r params$organism`

`r params$minsize`

`r params$confidence_level`

`r params$method`

**PROGENy** weights (_weightObj_) was `r params$pro_custom`

`r params$perm`
`r params$top`

The **network** (_netObj_) was `r params$omni`

The **perturbation nodes** (inputObj) were `r params$targets`

The selected **solver** was `r params$solver`.

#### The code
  
```{r, eval=FALSE}
carnival_result = runCARNIVAL( inputObj = iniciators,
                               measObj = tfList, 
                               netObj = cNET, 
                               weightObj = progenylist, 
                               solverPath = solver$spath, 
                               solver = solver$solver,
                               timelimit = 7200,
                               mipGAP = 0,
                               poolrelGAP = 0 )
```

### The results

#### Network visualisation

CARNIVAL produces a weigthed network that can be directly visualised. 

```{r, echo=FALSE, fig.width=10}
params$carnival_network
```

#### Enrichment analysis

A pathway/set enrichment analysis can be run over the results.

For this analysis, `r params$pea_custom`

`r params$pea_explanation`

`r params$pea_expl_barplot`

```{r, echo=FALSE, fig.width=10, eval=as.logical(params$active_pea), error=FALSE, message=FALSE, warning=FALSE}
params$barplot
```

`r params$pea_expl_volcano`

```{r, echo=FALSE, eval=as.logical(params$active_pea), error=FALSE, message=FALSE, warning=FALSE}
params$volcano
```
