---
title: "KinAct Analysis Report"
output: html_document
params:
  minsize: NA
  method: NA
  organism: NA
  selected_kinase: NA
  selected_sample: NA
  numberKinases: NA
  sample_plot: NA
  tf_plot: NA
  network_plot: NA
  heatmap_plot: NA
---

[KinAct](http://saezlab.github.io/kinact/) is a resource linking kinases to phosphorylation sites ( [Wirbel et al., 2018](https://link.springer.com/protocol/10.1007%2F978-1-4939-7493-1_6 ). 
It is fully integrated into Omnipath due to the addition of kinase-substrate interaction resources ( [Türei et al., 2021, 2016](http://europepmc.org/abstract/MED/27898060) ). 
Kinase activity estimation is performed using the same algorithm as DoRothEA to estimate activity scores ( [Alvarez et al., 2016](https://www.nature.com/articles/ng.3593) ). Instead of TF-target interactions, KinAct uses collections of kinase-substrate interactions and phosphoproteomic data instead of transcriptomic data.

### The analysis

The selected parameters:

- organism: `r params$organism`
- min size: `r params$minsize`
- method: `r params$method`

The code:

```{r, eval=FALSE}
dorothea::run_viper(kinase_matrix, 
                    kinact_regulon_human,
                    options =  list(minsize = minsize,
                                    method = method,
                                    eset.filter = FALSE,
                                    cores = 1,
                                    verbose = FALSE,
                                    nes = TRUE))
```

### The results

The computation yields a matrix with the normalised enrichment scores for each Kinase across all samples.

The heatmap provides a comprehensive overview of all contrasts/samples.
This heatmap includes the top `r params$numberKinases` selected TFs for the sample **`r params$selected_sample`** compared with the rest of the samples.

```{r, echo=FALSE, fig.width=10}
params$heatmap_plot
```

The bar plots show the activity of **`r params$selected_kinase`** for all given contrasts/samples;
and the top `r params$numberKinases` regulated TFs for sample **`r params$selected_sample`**.

```{r, echo=FALSE}
params$tf_plot

params$sample_plot
```

The interactions of `r params$selected_kinase` with its targets is shown in a network plot for sample `r params$selected_sample`.

Blue nodes indicate that the target is over-expressed and red nodes indicate that the target is down-regulated. The color of the edges represent the effect of the TF on its target (either activation or repression). The number of shown nodes can be changed by the corresponding widget.

```{r, echo=FALSE}
params$network_plot
```